I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-08 Paper/Paper_noProof.tex
Writing

%\usepackage[latin9]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
% \usepackage{esint}
\usepackage{array}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{url}
\usepackage{tikz}
\usepackage{calc}
\usetikzlibrary{positioning, arrows.meta,calc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\[
\begin{array}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  2.22 & 2.22  \\ \hline
	10  &  1.84 & 2.03  \\ \hline
	20  &  1.50 & 1.82  \\ \hline
	30  &  1.28 & 1.62  \\ \hline
	40  &  1.14 & 1.44  \\ \hline
	50  &  1.06 & 1.23  \\ \hline
\end{array}
\]

@@

\[
\begin{array}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  1.758 & 1.758  \\ \hline
	10  &  1.677 & 1.695  \\ \hline
	20  &  1.539 & 1.622  \\ \hline
	30  &  1.431 & 1.542  \\ \hline
	40  &  1.329 & 1.47  \\ \hline
	50  &  1.243 & 1.39  \\ \hline
\end{array}
\]

@@

The following table is the summary of 5 experiments.

\[
\begin{array}{c|c|cc|cc|cc|cc}

	\text{Network}  & \varepsilon&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\

  &  & \mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) &\mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
\end{array}
\]

@@

We do tests on 5 typical MNIST models.

>>>>

%\usepackage[latin9]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
% \usepackage{esint}
\usepackage{array}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{url}
\usepackage{tikz}
\usepackage{calc}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{algorithm}
	\caption{Process for length 3 + length 4}
	\KwData{Input data}
	\KwResult{Open node list}
	\While{condition}{
		Perform operation 1\;
		\If{condition}{
			Perform operation 2\;
		}
		\Else{
			Perform operation 3\;
		}
	}
\end{algorithm}

@@

\begin{table}
	\centering
	\begin{tabular}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  2.22 & 2.22  \\ \hline
	10  &  1.84 & 2.03  \\ \hline
	20  &  1.50 & 1.82  \\ \hline
	30  &  1.28 & 1.62  \\ \hline
	40  &  1.14 & 1.44  \\ \hline
	50  &  1.06 & 1.23  \\ \hline
\end{tabular}
\caption{}
\label{tab:example0}
\end{table}

\vspace*{-8ex}

@@

\begin{table}
	\centering
	\begin{tabular}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  1.758 & 1.758  \\ \hline
	10  &  1.677 & 1.695  \\ \hline
	20  &  1.539 & 1.622  \\ \hline
	30  &  1.431 & 1.542  \\ \hline
	40  &  1.329 & 1.47  \\ \hline
	50  &  1.243 & 1.39  \\ \hline
\end{tabular}
\caption{}
\label{tab:example1}
\end{table}

@@

\begin{table}
	\centering
	\begin{tabular}{c|c|cc|cc|cc|cc}

	\text{Network}  & $\varepsilon$&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\

  &  & \textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) &\textrm{Ver}.\% & \textrm{Time}(s) & \textrm{Ver}.\% & \textrm{Time}(s) \\ \hline

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
\end{tabular}
\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
\label{tab:example}
\end{table}

@@
